The paper states that only looking for the improvement on LLm when looking to improve a rag is not the only best idea. In this paper, they emphasizes that retriever component should be where we need to
focus on when looking to improve a rag system. It is why they have implemented a Blended RAG where we find a combination of different retrievers. First, there is the Keyword search retriever (BM25) which 
is a traditional retriever that looks for exact matches of keywords in the query and the documents. It uses fuzzy matching to increase the performance. Then, the Dense retriever search with KNN embeddings. 
It is a retriever that here looking for contextual similarity between the query and the documents using embeddings. Finally a Sparse semantic search retriever(ELSER/ SParse Encoder). It is a combination of
semantic and similarity search. It looks to better understand the real intention behind the question and the contexts and then find better matching documents. Even more, each request and document is associated
with a large trianing set of data. It allows the to better improve the context around the concept and then find better matching documents. With that they combiend these retrievers with different versions of 
multimatch queries. As the infomration is spread out in the different field of the text , different types of thecniques exists to better select the best fiels for the answer. We can find Best Fields that will
find the best field over the other having the best matches for the query, Cross Fields that will try to combine the different matches across the field to better give the answer. Most field will use all the matches
to better describe the document. Each latching field will contribute, etc. The "Blended" comes to this combination of Retriever and multi-match techniques . They underlignesd the imoportance of how the query was executed.
The best retriver found was Sparse Encoder + Best Fields across multiple datsets. It yields results against previous methods implmented as . When implemented in Rag, it outperms previous rag method. The results whereobtain using Squad 
a known large dataser known to have text coming from wikipedia with specific designed questions for them. It is larlegly used to compare the performance of Rag. The Rag yields incridible result in a lot of field ( Exact Match, Rag, etc.)
showing it reliability as a new method.





Methodology
Due to the heavyness of the model used in the papers we wanted to compare the different approach using a smaller computational needing pipeline. Based on the paper on the hybrid search, Stanford Question Answering Dataset (SQuAD) was used to better be able to compare the
different approach. "The Squad is Stanford Question Answering Dataset (SQuAD) is a reading comprehension dataset, consisting of questions posed by crowdworkers on a set of Wikipedia articles, where the answer to every question is a segment of text, or span, from the 
corresponding reading passage, or the question might be unanswerable." \cite{huggingface} We first extracted from the dataset of 100k questions the first 500 ones. Enough to have relevent dataset but not to much so it is still feasible at our scale. A file containing 
the question and answers was stored for the future accuracy comparison and a file having only the different context was stored. In the Hybrid paper, they used this LLM " FLAN-T5-XXL." It is really demanding model a lot of RAMS. We decided to use instead gemini-2.5-flash
as it is a performant and known model today. We created a server using FAST api . The context for the rag was the one From the contexts saved with chromadb earlier. The are tokenize using BM250api. It is the same used in the paper BM25 however this one is available in python libraiy.

Once The question is written in the api with the methid it is stored The query is vectorized using tect_embedding-004" form google As 
\subsection{Hybrid} 
Same as in the paper query tokenized then score obtain with bm25 The top 25 is chosen The space vectors then rrf score instead of ... beacause ....

\subsection{reranking }
done using library Cross encoder allowing ... return only the top

\subsection(hyde search)
done using prompt "    hyde_prompt = f"""Write a factual paragraph that would likely appear in a document answering the following question. answer generated with gemini flash and answer given as  a query 
"
